Evaluation of performances

### 2019-09-19 analysis/eval-performance.Rmd
wflow_publish(knitr_in("analysis/eval-performance.Rmd"), view = FALSE, verbose = TRUE)

@@

@@

comb %>%
  ggplot(aes(x = rmse.test.rmse, y = learner_group)) +
  geom_beeswarm(groupOnX = FALSE, aes(color = filter), size = 3) +
  facet_wrap(~task.id) +
  scale_color_nejm() +
  labs(x = "RMSE", y = "Task", color = "Filter") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(30, 45)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    axis.text.y = element_text(angle = 45),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```

>>>>

saveRDS(table1, "code/98-paper/presentation/table-perf.rda")

@@

saveRDS(table2, "code/98-paper/presentation/table-best-learner-per-task.rda")

@@

comb %>%
  ggplot(aes(x = rmse.test.rmse, y = learner_group)) +
  geom_beeswarm(groupOnX = FALSE, aes(color = filter), size = 3) +
  facet_wrap(~task.id) +
  scale_color_nejm() +
  labs(x = "RMSE", y = "Task", color = "Filter") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(30, 47)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    axis.text.y = element_text(angle = 45),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```
